Deuteron Electro-Disintegration at Very High Missing Momenta

### 2020-04-09 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/body.tex
updated

contributions from normalization uncertainties for each setting were determined to be (on average): tracking efficiencies ($0.40 \%$-HMS, $0.59 \%$-SHMS ), proton loss in HMS ($0.49 \%$), target boiling ($0.39 \%$), total live time ($3.0 \%$) and total charge ($2.0\%$)
for an overall normalization uncertainty added in quadrature of about 3.7 $\%$ per setting. \\

@@

\begin{figure}[ht!]

>>>>

contributions from normalization uncertainties for each setting were determined to be (on average): tracking efficiencies ($0.40 \%$-HMS, $0.59 \%$-SHMS ),
and target boiling ($0.38 \%$) which were added in quadrature and determined to be about 0.81 $\%$ per setting. The systematic uncertainties due to
proton loss in HMS ($0.49 \%$), total live time ($3.0 \%$), and total charge ($2.0\%$) were the same for every setting and thus were added (in quadrature)
as an overall normalization constant to the final result.\\

@@

\begin{figure}
